\section{Steps taken for career growth of the company}
\subsection{Steps taken by TVS Motors}

These are some steps taken for the growth of the company \cite{TVS_ANNUAL_REPORT}.

\begin{enumerate}
	\item \textbf{Total Quality Management (TQM)}: Utilising digital and AI initiatives, the Company continuously enhances customer experience processes and improves forecasting accuracy at the front end.
	
	\item \textbf{Cost and Price Management}: The Company provides high-value offerings to consumers achieved through aggressive waste reduction and quality improvement strategies such as value engineering, modularity, lightweight, alternative materials, localisation, and process innovation.
	
	\item \textbf{Research and Development}: Investing in building world-class in-house skill sets	in technology research, product design and development, an exclusive team of specialised engineers has been formed for in-house software development.
	\item \textbf{Digital and AI Technologies}: The Company considers Digital and AI as a key organisation-wide accountability area. Currently, it prioritises digitalising the Company’s operations in customer experience, retail and service management, manufacturing and supply chain, New Product Introduction (NPI), and enterprise functions.
	
\end{enumerate}


\subsection{Steps taken by Hero MotoCorp}

These steps were take by the board of chairmen at Hero MotoCorp to improve the status of the company.

\begin{enumerate}
	
\item \textbf{Enterprise-wide Quality}: Robust quality management systems relentlessly pursue continuous improvement, ensuring quality is incorporated across all our products, processes, systems, and services.
100\% of the facilities are ISO 9001 certified.\\
\item \textbf{Quality Sensitisation and Awareness}: Initiative focus
on developing the right mindset among all stakeholders, while
providing opportunities for young talent to showcase innovative
ideas and critical thinking to a wider organisational audience.\\
\item \textbf{Supply Chain Excellence}: They consistently assist their supply chain partners in improving their quality processes by sharing their technical expertise. Their Supply Chain Partner Quality Manual lays down guidelines for effective functioning and establishes stringent checkpoints along	product development and mass production stages.
\item \textbf{Vehicle Recall Policy and Traceability}: Following the roll-out of the Vehicle Recall Policy by the
Government of India in 2021, Hero MotoCorp swiftly
developed a framework to manage and execute a mandatory
vehicle recall as prescribed.

\end{enumerate}