\section{Industrial psychologist}
\subsection{Details at TVS}

\textbf{Name}: Lakshmiprabha A\\
\textbf{Shoert Description}: HR Business Partner @ TVS Motor Company | Manager - HRD | HR Digital Transformation\\
\textbf{Description}:  HR Professional with 10+ years of experience in Talent Acquisition, Performance Management System, HR Digital Transformation, Compensation \& Benefits, and Employee Engagement\\
\textbf{LinkedIn}: https://www.linkedin.com/in/lakshmiprabha-a-4660136a/

Lakshmiprabha A, an industrial psychologist, has made important contributions to TVS Motors by applying psychological principles to improve workplace dynamics and enhance employee performance. In her role, she focuses on understanding human behavior in industrial settings, helping TVS Motors optimize its workforce management, boost productivity, and create a positive organizational culture. Her insights into employee motivation, leadership development, and team dynamics have likely supported TVS Motors in fostering a more engaged and efficient workforce. By applying psychological tools and assessments, she may also contribute to the selection and development of leaders within the company, promoting long-term success.
Her contributions have helped TVS Motors align its human resources strategies with business goals, ensuring that employees' well-being and productivity are maximized in a competitive industry.

\subsection{Details at Hero MotoCorp}

\textbf{Name}: Dr. Kamal Karamchandani\\
\textbf{Description}: Expertise in business planning, strategic sales-marketing, channel management / development / productivity, CRM, multi-cultural diversity, manpower development, change management, coaching, behavioral guidance\\
\textbf{LinkedIn}: https://www.linkedin.com/in/dr-kamal-karamchandani-76b13618/

Dr. Kamal Karamchandani, an ex-industrial psychologist, played a key role at Hero MotoCorp, one of the largest two-wheeler manufacturers in the world. In his capacity as an industrial psychologist, Dr. Karamchandani applied behavioral science techniques to enhance organizational effectiveness and employee well-being. He was involved in improving employee performance, leadership development, and organizational culture at Hero MotoCorp. His work likely contributed to better employee engagement, streamlined HR processes, and improved collaboration across teams.