\section{Recruitment and Selection}
%TVS : \\
%Recruitment Process: Comprehensive stages including screening, interviews, and assessments.\\Talent Acquisition: Focus on engineering, software development, data analytics, and automotive technology.\\Career Development: Opportunities include leadership training and cross-functional roles.
%\\\\
%Hero : \\
%56\% of recruitment is campus recruitment (external).\\ 24\% by recruitment agencies (external),\\ 10\% from company website.\\ 10\% from internal sources (employee referral) and other sources. \\\\
%Selection process is moderate. Employees find good work culture.

\subsection{TVS Motors}

TVS Motor’s recruitment strategy aims to attract top talent in the automotive and technology sectors, ensuring a skilled and diverse workforce:

\subsubsection{Recruitment}
The company’s recruitment process includes multiple stages such as initial screening, interviews, and assessments to evaluate candidate competencies and cultural fit. TVS Motor emphasizes diversity and inclusivity in hiring practices, promoting equal opportunities and a conducive work environment.

\subsubsection{Talent Acquisition}
In FY 2023-24, TVS Motor focused on talent acquisition to strengthen its capabilities in electric mobility and digital transformation. The recruitment drive targeted professionals with expertise in engineering, software development, data analytics, and automotive technology.

\subsubsection{Career Development}
Once on boarded, employees undergo comprehensive on boarding and training programs through the Institute of Quality and Leadership (IQL). Career development opportunities include cross-functional rotations, leadership training, and continuous learning initiatives to nurture talent and drive organizational growth.

\subsection{Hero MotoCorp}
\subsubsection{Recruitment}
Hero MotoCorp follows a structured recruitment process to attract a diverse range of candidates who align with the company's values and operational needs. The recruitment strategy emphasizes understanding the skills required for various roles and finding suitable candidates from diverse backgrounds. The process typically involves the following steps:

\begin{enumerate}
	\item \textbf{Job Analysis and Description}: Before initiating recruitment, a thorough analysis of job roles is conducted. This includes defining job responsibilities, required qualifications, and desired competencies to ensure clarity in the recruitment process.
	
	\item \textbf{Sourcing Candidates}: Hero MotoCorp utilizes various channels for sourcing candidates, including online job portals, campus recruitment drives, employee referrals, and recruitment agencies. This multi-channel approach helps reach a wide audience and attract a diverse pool of talent.
	
	\item \textbf{Initial Screening}: Resumes and applications are screened to shortlist candidates based on their qualifications and experience. This step ensures that only the most suitable candidates progress to the next stages of the selection process.
\end{enumerate}


\subsubsection{Talent Acquisition}
Hero MotoCorp’s talent acquisition process is focused on aligning the right candidates with the company’s strategic goals and culture. Key elements of this process include:

\begin{enumerate}
	\item \textbf{Interviews}: Shortlisted candidates undergo a series of interviews, which may include HR interviews, technical assessments, and managerial interviews. These interviews are designed to assess candidates' skills, cultural fit, and overall compatibility with the organization's values.

	\item \textbf{Assessment Tests}: Depending on the role, candidates may be required to complete various assessment tests that evaluate their technical skills, problem-solving abilities, and behavioral competencies. This helps in making informed decisions about their suitability for the role.

	\item \textbf{Reference Checks}: For final candidates, reference checks are conducted to verify their employment history and gather insights into their work ethic and performance from previous employers.
\end{enumerate}

\subsubsection{Selection}
The selection process at Hero MotoCorp aims to ensure that the best candidates are chosen for the available positions. This involves:

\begin{enumerate}
	\item \textbf{Final Interview}: Candidates who perform well in previous stages may be invited for a final interview with senior management or department heads. This step provides a platform to discuss expectations, career aspirations, and any remaining questions.

	\item \textbf{Job Offer}: Successful candidates receive a formal job offer that includes details about their role, salary, benefits, and other relevant terms of employment. The HR team ensures that the offer is competitive and aligns with industry standards.

	\item \textbf{Onboarding}: Once the candidate accepts the offer, Hero MotoCorp initiates the onboarding process, which includes orientation sessions, training programs, and familiarization with company policies and culture. This ensures a smooth transition for new employees into their roles.
\end{enumerate}

\subsubsection{Career Development}
Hero MotoCorp places significant emphasis on career development and employee growth. The company invests in various initiatives to support its employees in their professional journeys:

\begin{enumerate}
	\item \textbf{Training and Development}: Ongoing training programs are offered to employees to enhance their skills and competencies. This includes technical training, leadership development, and soft skills training to prepare employees for future roles.
	
	\item \textbf{Performance Management}: Regular performance appraisals are conducted to provide employees with feedback on their performance and identify areas for improvement. This helps in setting career goals and aligning individual aspirations with organizational objectives.
	
	\item \textbf{Succession Planning}: Hero MotoCorp has a robust succession planning process to identify and develop high-potential employees for leadership positions. This ensures that the company has a pipeline of talent ready to step into key roles as they become available.
	
	\item \textbf{Diversity and Inclusion Initiatives}: The company is committed to fostering a diverse and inclusive workplace. Programs aimed at promoting gender diversity and inclusion are integral to the recruitment and career development processes.
\end{enumerate}