\section{Rules and regulations}

\subsection{Rules needed to be followed by TVS employees}

	Here are some of the rules that the employees of TVS Motors should follow. The rules are set up to \textit{maximize efficiency, improve performance and remove any form of corruption from the company }\cite{TVS_ANNUAL_REPORT}. 

\begin{enumerate}
	\item \textbf{Adherence to Core Values}: Employees must uphold TVS's core values of trust, customer obsession, value maximization, speed and agility, exactness, and a disruptive mindset in all aspects of their work.
	
	\item \textbf{Commitment to Transparency and Fairness}: Employees are expected to demonstrate transparency and fairness in all dealings, ensuring ethical behavior and accountability at every level of operation.
	
	\item \textbf{Customer-Centric Approach}: Employees must proactively understand and address customer needs, aiming to exceed customer expectations and deliver high-quality service and products.
	
	\item \textbf{Compliance with Policies and Regulations}: Employees must strictly follow all company policies, statutory labor laws, environmental regulations, and health and safety standards applicable to their role.
	
	\item \textbf{Data Privacy and Confidentiality}: Employees are responsible for safeguarding company and customer data, ensuring compliance with data privacy and cybersecurity policies to protect digital assets.
	
	\item \textbf{Sustainability and Environmental Responsibility}: Employees should actively contribute to the company’s sustainability goals by reducing resource consumption, minimizing waste, and following environmentally friendly practices at work.
	
	\item \textbf{Health and Safety Compliance}: Employees are required to follow all workplace safety guidelines, including the use of personal protective equipment (PPE) and participation in regular safety training programs.
	
	\item \textbf{Continuous Learning and Development}: Employees are encouraged to engage in continuous professional development through the company's training programs and initiatives to improve their skills and adapt to evolving business needs.
	
	\item \textbf{Non-Discrimination and Inclusivity}: TVS promotes diversity and inclusion, so employees must foster a respectful and inclusive work environment, free from discrimination based on gender, race, disability, or background.
	
	\item \textbf{Whistleblower Policy Adherence}: Employees are encouraged to report any unethical practices or violations of company policies in good faith, under the company's Whistleblower Policy, without fear of retaliation
\end{enumerate}

\subsection{Rules needed to be followed by Hero employees}

Hero MotoCorp Limited has established a comprehensive Code of Conduct \cite{hero-code-of-conduct} to maintain high standards of business conduct and ethics. This code applies to all Directors and Employees, including associates working on third-party contracts or payroll. It is designed to promote efficiency, responsiveness, and consistency in behavior and decision-making while reducing risks associated with harmful conduct. The following rules and regulations are crucial for all members of Hero MotoCorp to uphold the company's values and maintain its reputation:

\begin{enumerate}
	\item Avoid and disclose any actual or potential conflicts of interest that may interfere with the company's interests.
	\item Do not accept gifts, perks, services, or entertainment from suppliers or customers exceeding a monetary value of Rs. 2,500, and only accept generic gifts during festivals.
	\item Protect company assets, including confidential information, funds, and equipment, using them only for legitimate business purposes.
	\item Maintain the highest standards of personal and professional integrity, honesty, and ethical conduct in all company-related activities.
	\item Ensure accurate and reliable financial and non-financial reporting, fully disclosing all assets and liabilities.
	\item Maintain a work environment free from discrimination, harassment, and unsafe conditions, treating all individuals with dignity and respect.
	\item Comply fully with all applicable laws and regulations, including fair trade and competition laws.
	\item Refrain from offering company funds or property as donations to government or non-government agencies to obtain favors or influence business decisions.
	\item Minimize the environmental impact of the company's activities and preserve the surrounding natural environment where possible.
	\item Do not engage in political activities or campaigns on behalf of the company, and avoid making charitable contributions to influence business decisions.
\end{enumerate}